Mutation loads in rheumatoid arthritis data from SComatic

### 2024-02-01 scomatic/reports/driver_coverage.Rmd
add nextflow wrapper for driver_coverage

---
title: "Mutation loads in rheumatoid arthritis data from SComatic"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: false
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
    rerun: true
---

@@

We use `samtools depth` to get the coverage of each site in the drivers, both across each sample and within each cell type in each sample.

>>>>

---
title: "Mutation loads in rheumatoid arthritis data from SComatic"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: false
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
    rerun: true
    gene: NULL
    coords: NULL
---

@@

We use `samtools depth` to get the coverage of each site in the drivers, both across each sample and within each celltype in each sample.
